Evaluation of the repository

### 2024-11-28 pages/paper_evaluation.qmd
fix(images): modified scale so images are 300 dpi at 14cm width

# Save figure as 300DPI static image for use in article
pio.write_image(stress_chart, '../images/stress_criteria.png',
                width=2.8*300, height=2.5*300, scale=1)
```

@@

# Save figure as 300DPI static image for use in article
pio.write_image(ispor_chart, '../images/ispor_criteria.png',
                width=2.5*300, height=2*300, scale=1)

>>>>

# Save figure as 300DPI static image for use in article
pio.write_image(stress_chart, '../images/stress_criteria.png',
                width=2.8*300, height=2.5*300, scale=1.97)
```

@@

# Save figure as 300DPI static image for use in article
pio.write_image(ispor_chart, '../images/ispor_criteria.png',
                width=2.5*300, height=2*300, scale=2.2)

### 2024-11-28 pages/repo_evaluation.qmd
fix(images): modified scale so images are 300 dpi at 14cm width

# Save figure as 300DPI static image for use in article
pio.write_image(stars_chart, '../images/stars_criteria.png',
                width=2.5*300, height=1.8*300, scale=1)
```

>>>>

# Save figure as 300DPI static image for use in article
pio.write_image(stars_chart, '../images/stars_criteria.png',
                width=2.5*300, height=1.8*300, scale=2.2)
```
